Who does big team science?

### 2022-05-06 04.manuscript.tex
install stuff!
install stuff!

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Big Team Science}
\keywords{big team, science, authorship, credit\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

@@

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

@@

\begin{itemize}
\tightlist
\item
  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(53) = 1.71, \emph{p} = .092.
\item
  The variance parameter was \(SD\) = 7.99.
\item
  The slope for variance across years was \emph{b} = 0.01, \emph{SE} = 0.48, \emph{t}(23) = 0.02, \emph{p} = .983.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(15) = 1.59, \emph{p} = .132.
\item
  The variance parameter was \(SD\) = 8.88.
\item
  The slope for variance across years was \emph{b} = 0.16, \emph{SE} = 0.61, \emph{t}(2) = 0.26, \emph{p} = .821.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The slope for year of first degree was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(35) = 5.14, \emph{p} = \textless{} .001.
\item
  The variance parameter was \(SD\) = 7.77.
\item
  The slope for variance across years was \emph{b} = 0.03, \emph{SE} = 0.82, \emph{t}(14) = 0.04, \emph{p} = .971.
\end{itemize}

>>>>

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{big team, science, authorship, credit\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\shorttitle{Big Team Science}

@@

\abstract{%
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

@@

\begin{itemize}
\tightlist
\item
  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(53) = 0.93, \emph{p} = .358.
\item
  The variance parameter was \(SD\) = 8.02.
\item
  The slope for variance across years was \emph{b} = 0.01, \emph{SE} = 0.47, \emph{t}(23) = 0.02, \emph{p} = .984.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(15) = 1.04, \emph{p} = .315.
\item
  The variance parameter was \(SD\) = 8.88.
\item
  The slope for variance across years was \emph{b} = 0.16, \emph{SE} = 0.61, \emph{t}(2) = 0.26, \emph{p} = .821.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The slope for year of first degree was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(35) = 2.93, \emph{p} = .006.
\item
  The variance parameter was \(SD\) = 7.86.
\item
  The slope for variance across years was \emph{b} = 0.02, \emph{SE} = 0.82, \emph{t}(14) = 0.02, \emph{p} = .982.
\end{itemize}
